Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-21 paper/main.tex
working on methods (knowledge traces and maps)

% \begin{figure}[tp]
% \centering
% \includegraphics[width=0.8\textwidth]{figs/content-mastery}
% \caption{\textbf{Caption.} Placeholder text.}
% \label{fig:demo}
% \end{figure}

@@

As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
corpus of documents using overlapping sliding windows that span each video's
transcript. Khan Academy videos are hosted on the YouTube platform, and all
YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
to derive a timestamped transcript of any detected speech in the video. The
resulting transcripts contain one timestamped row per line, and each line
generally corresponds to a few seconds of spoken content from the video. We
defined a sliding window length of (up to) $w = 30$ transcript lines, and we
assigned each window a timestamp according to the midpoint between its first
and last lines' timestamps. These sliding windows ramped up and down in length
at the very beginning and end of the transcript, respectively. In other words,
the first sliding window covered only the first line from the transcript; the
second sliding window covered the first two lines; and so on. This ensured that
each line of the transcript appeared in the same number ($w$) of sliding
windows. We treated the text from each sliding window as a single ``document,''
and we combined these documents across the two videos' windows to create a single
training corpus for the topic model.  The top words from each of the 15 discovered
topics may be found in Table~\topics.

@@

@@

>>>>

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/content-mastery}

    \caption{\textbf{Estimating moment-by-moment knowledge acquisition.}
    \textbf{A. Moment-by-moment knowledge about the \textit{Four Fundamental
    Forces}}. Each trace displays the weighted proportion of correctly answered
    questions about the content reflected in each moment of the lecture (see
    \textit{Estimating dynamic knowledge traces}), using responses from one
    quiz (color). The traces are averaged across participants. \textbf{B.
    Average estimated knowledge about the \textbf{Four Fundamental Forces}.}
    Each bar displays the across-timepoint average knowledge, estimated using
    the responses to one quiz's questions. \textbf{C. Moment-by-moment
    knowledge about the \textit{Birth of Stars}}. The panel is in the same
    format as Panel A, but here the knowledge estimates are for the
    moment-by-moment content of the \textit{Birth of Stars} lecture. \textbf{D.
    Average estimated knowledge about the \textit{Birth of Stars}.} The panel
    is in the same format as Panel B, but here the knowledge estimates are for
    the content of the \textit{Birth of Stars} lecture. All panels: error
    ribbons and error bars denote 95\% confidence intervals, estimated across
    participants.}

    \label{fig:knowledge-timeseries}
    \end{figure}

@@

As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
corpus of documents using overlapping sliding windows that span each video's
transcript. Khan Academy videos are hosted on the YouTube platform, and all
YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
to derive a timestamped transcript of any detected speech in the video. The
resulting transcripts contain one timestamped row per line, and each line
generally corresponds to a few seconds of spoken content from the video. We
defined a sliding window length of (up to) $w = 30$ transcript lines, and we
assigned each window a timestamp according to the midpoint between its first
and last lines' timestamps. These sliding windows ramped up and down in length
at the very beginning and end of the transcript, respectively. In other words,
the first sliding window covered only the first line from the transcript; the
second sliding window covered the first two lines; and so on. This insured that
each line of the transcript appeared in the same number ($w$) of sliding
windows. We treated the text from each sliding window as a single ``document,''
and we combined these documents across the two videos' windows to create a single
training corpus for the topic model.  The top words from each of the 15 discovered
topics may be found in Table~\topics.

@@

We used the following equation to estimate each participant's knowledge about
timepoint $t$ of a given lecture, $\hat{k}(t)$:
\begin{equation} 
    \hat{k}(t) = \frac{\sum_{i \in \mathrm{correct}}\mathrm{ncorr}(t, i)}{\sum_{j = 1}^N \mathrm{ncorr}(t, j)},
    \label{eqn:prop}
\end{equation}
where

\begin{equation} 
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation} 
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints and questions across both lectures and all three question sets.

Intuitively, $\mathrm{ncorr}(x, y)$ is the correlation between two topic
vectors (e.g., the topic vector from one timepoint in a lecture, $x$, and the
topic vector for one question, $y$), normalized by the minimum and maximum
correlations (across all timepoints and questions) to range between 0 and 1,
inclusive. Equation~\ref{eqn:prop} then computes the weighted average
proportion of correctly answered questions about the content presented at
timepoint $t$, where the weights are given by the normalized correlations
between timepoint $t$'s topic vector and the topic vectors for each question.
The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
correlations) insures that every question (except the least-relevant question)
contributes some non-zero amount to the knowledge estimate.

@@

\begin{equation}
    \hat{k}(x) = \frac{\sum_{i \in \mathrm{correct}} \mathrm{RBF}(x, q_i, \lambda)}{\sum_{j = 1}^N \mathrm{RBF}(x, q_j, \lambda)},
\end{equation}
where
\begin{equation}
    \mathrm{RBF}(x, \mu, \lambda) = \exp\left\{-\frac{||x - \mu||^2}{\lambda}\right\}.
\end{equation}
